### 2018-04-25 Docs/Thesis/docs/appendix/appendixB.tex
thesis update

\chapter{Traffic Generators Survay}
\label{ap:traffic-gen-survey}

@@

>>>>

\chapter{Traffic Generators Survey}
\label{ap:traffic-gen-survey}

@@

\section{Validation of Ethernet traffic generators: some use cases}

In this section we list some use cases of validation of Ethernet traffic generators. Our validation methods used on chapter~\ref{ch:modeling-evaluation} and~\ref{ch:validation} were based on them. We are going to present seven different study cases on validation of related traffic generators. They are Swing\cite{swing-paper}, Harpoon\cite{harpoon-paper}, D-ITG\cite{ditg-paper}, sourcesOnOff\cite{sourcesonoff-paper}, MoonGen\cite{moongen-paper}, LegoTG\cite{legotg-paper} and NFPA\cite{nfpa-paper}.

\subsubsection{Swing}
Swing\cite{swing-paper} is at present, one of the main references of realistic traffic generation.  The authors extracted bidirectional metrics from a network link of synthetic traces. Their goals were to get realism, responsiveness, and randomness.  They define realism as a trace that reflects the following characteristics of the original:

\begin{itemize}
	\item Packet inter-arrival rate and burstiness across many time scales;
	\item Packet size distributions;
	\item Flow characteristics as arrival rate and length distributions;
	\item Destination IPs and port distributions.
\end{itemize}

The traffic generator uses a structural model the account interactions between many layers of the network stack. Each layer has many control variables, which is randomly generated by a stochastic process.  They begin the parameterization, classifying tcpdump\cite{web-libpcap} \textit{pcap}  files with the data, they are able to estimate parameters.

They validate the results using publicly available traffic traces, from Mawi\cite{web-mawi} and CAIDA\cite{web-caida}. On the paper, the author focuses on these validation metrics:

\begin{itemize}
	\item Comparison of estimated parameters of the original and swing  generated traces;
	\item Comparison of aggregate and per-application bandwidth and packets per seconds ;
	\item QoS metrics such as two-way delay and loss rates;
	\item Scaling analysis, via Energy multiresolution energy analysis.
\end{itemize}

To the vast majority of the results, both original and swing traces results were close to each other. Thus,  Swing was able to match aggregate and burstiness metrics, per byte and per packet, across many timescales.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Harpoon}

Harpoon\cite{harpoon-validation}\cite{harpoon-paper} is a traffic generator able to generate representative traffic at IP \textit{flow level}. It can generate TCP and IP with the same byte, packet, temporal and spatial characteristics measured at routers. Also, Harpoon is a self-configurable tool, since it automatically extracts parameters from network traces. It estimates some parameters from original traffic trace: file sizes, inter-connection times, source and destination IP addresses, and the number of active sessions.

As proof of concept \cite{ harpoon-validation}, the authors compared statistics from original, and harpoon's generated traces. The two main types of comparisons: diurnal throughput, and for stochastic variable CDF and frequency distributions. Diurnal throughput refers to the average bandwidth variation within a day period.  In a usual network, during the day the bandwidth consumption is larger, and at night smaller. Also, they compared:

\begin{itemize}
	\item CDF of bytes transferred per 10 minutes
	\item CDF of packets transferred per 10 minutes
	\item CDF of inter-connection time
	\item CDF of file size
	\item CDF of flow arrivals per 1 hour
	\item Destination IP address frequency
\end{itemize}

In the end, they showed the differences in throughput evaluation of a Cisco 6509 switch/router using Harpoon and a constant rate traffic generator.  
Harpoon was proven able to give close CDFs, frequency and diurnal throughput plots compared to the original traces. Also, the results demonstrated that Harpoon provides a more variable load on routers, compared to constant rate traffic. It indicates the importance of using realistic traffic traces on the evaluation of equipment and technologies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{D-ITG}

D-ITG\cite{ditg-paper} is a network traffic generator, with many configurable features. The tool provides a platform that meets many emerging requirements for a realistic traffic generation. For example, multi-platform, support of many protocols, distributed operation, sending/receiving flow scalability, generation models, and analytical model based generation high bit/packet rate. You can see different analytical and models and protocols supported by D-ITG at table ~\ref{tab:trafficgen-list1}.

We will focus on the evaluation of realism on analytical model parameterization.  It is a synthetic replication of a LAN party of eight players of Age of Mythology \footnote{\href{https://www.ageofempires.com/games/aom/}{https://www.ageofempires.com/games/aom/}}. They have captured traffic flows during the party. Then, they modeled its packet size and inter-packet time distributions. They show that the synthetic traffic and the analytical model have similar curves of packet size and inter-packet time; thus it can approximate the empirical data. Also, the mean and the standard deviation of the bit rate of the empirical and synthetic data are similar.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{sourcesOnOff}

Varet et al. \cite{sourcesonoff-paper} create an application implemented in C, called SourcesOnOff. It models the activity interval of packet trains using probabilistic distributions. To choose the best stochastic models, the authors have captured traffic traces using TCPdump. Then the developed tool can figure out what distribution (Weibull, Pareto, Exponential, Gaussian, etc.) fits better the original traffic traces. It uses the Bayesian Information Criterion (BIC) for distance assessment. It tests the smaller BIC for each distribution and selects it as the best choice. It ensured good correlation between the original and generated traces and self-similarity.

The validation methods used on sourcesOnOff are: 
\begin{itemize}
	\item Visual comparison between On time and Off time of the original trace and the stochastic fitting;
	\item QQplots, which aim to evaluate the correlation between inter-trains duration of real and generated traffic;
	\item Measurement of Autocorrelation\footnote{
		The autocorrelation functions measures the correlation between data samples $y_{t}$ and $y_{t + k}$, where $k =0, ..., K$, and the data sample $\{y\}$  is generated by a stochastic process.

		According to \cite{book-time-series-analysis}, the autocorrelation for a lag $k$ is:

		\begin{equation}
		r_{k} = \frac{c_{k}}{c_{0}}
		\end{equation}

		where

		\begin{equation}
		c_{k} = \frac{1}{T - 1}\sum_{t = 1}^{T - k} (y_{t} - \bar{y})(y_{t+k} - \bar{y})
		\end{equation}

		and $c_{0}$ is the sample variance of the time series. 
	} of the measured throughput of the real and synthetic traffic;
	\item Hurst exponent computation of the real and the synthetic trace;
\end{itemize}

The results pointed to an excellent stochastic fitting, but better for On-time values. On the other hand, the correlation value of the QQplot was more significant on the Off time values (99.8\% versus 97.9\%). In the real and synthetic traces, the autocorrelation of the throughput remained between an upper limit of 5\%. Finally, the ratio between the evaluated Hurst exponent always remained smaller than 12\%.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{MoonGen}

MoonGen\cite{moongen-paper} is a high-speed scriptable paper capable of saturating 10 GnE link with 64 bytes packets, using a single CPU core. The authors have built it over DPDK and LuaJit, enabling the user to have high flexibility on the crafting of each packet, through Lua scripts. It has multi-core support and runs on commodity server hardware. It can test latency with sub-microsecond precision and accuracy, using hardware timestamping of modern NICs cards. The Lua scripting API enable the implementation and high customization along with high-speed. This includes the controlling of packet sizes and control of inter-departure times.

The authors evaluated this traffic generator focused on throughput metrics, rather than others. Also, they have small packet sizes (64 bytes to 256), since the per-packet costs dominate. In their work, they were able to surpass 15 Gbit/s with an XL710 40 GbE NIC. Also, they achieve throughput values close to the line rate with packets of 128 bytes, and 2 CPU cores.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LegoTG}

Bartlett et al.\cite{legotg-paper} implements a modular framework for composing custom traffic generation, called LegoTG. As argued by the authors (and by this present work), automation of many aspects of traffic generation is a desirable feature. The process of how to generate proper background traffic may become research by itself. Traffic generators available today offer a single model and a restricted set of features into a single code base, makes customization difficult.

The primary purpose of their experiment is to show how LegoTG can generate background traffic, only. Also, it shows how realistic background traffic can influence research conclusions. The test chosen is one of the use cases proposed for Swing\cite{background-traffic-matter}, and it evaluates the error on bandwidth estimation of different measurement tools. It shows that LegoTG can provide secure and custom traffic generation.

### 2018-04-25 Docs/Thesis/docs/chapter1.tex
update
thesis update

Emerging technologies such as SDN and NFV are great promises and would change drastically the development and operation of computer networks. However, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior. Since it is expected virtualization to impact negatively on performance, these VNFs have to keep its degradation as small as possible. Guarantee the Service Layer Agreements on emerging scenarios is now a harder question. There is a demand for more reliable methods to ensure the SLAs, over different types of loads.

It is already a well-known fact that the type of traffic used on performing tests matters. Studies show that a realistic Ethernet traffic provides a different and more variable load characteristics on routers\cite{harpoon-validation}, even with the same mean bandwidth consumption. It indicates that tests with constant bit rate traffic generator tools are not enough for a complete validation of new technologies. There are many reasons for this behavior, which includes burstiness and packet sizes.

A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}, and  measurement accuracy\cite{legotg-paper} \cite{background-traffic-matter}. Another key question is how applications will deal with packets. It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}. A realistic synthetic traffic must not have a single packet-size but must use a distribution \cite{packet-distribution-model}.

Realistic workload generators are also essential security research\cite{ditg-paper}.  Generation of realistic workloads is important in the evaluation of firewall middleboxes. It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}. Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.

Another critical point is the flow-oriented operation of SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller.  Also the SDN switches have a flow-oriented operation. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider. Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How VNFs and virtualized middle-boxes and SDN testbeds will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is a relevant subject.

@@

The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation, and enable controll of different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, On/Off periodos, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.

Some traffic generator tools offer support emulation of single application workloads. However, this does not correspond to real complex scenarios. Other tools work as packet replay engines, such as TCPreplay and TCPivo. Although in that way is possible to produce a realistic workload at high rates, it comes with some issues. First, the storage space required becomes huge for long-term and high-speed traffic capture traces. Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources.

Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper}, sourcesOnOff\cite{sourcesonoff-paper}, and MoonGen. All of them offer a complex configuration framework, but its custumization is all up to the user. So, there is no simple way for the user to create an synthetic realistic traffic scenario.

We also have available a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others. These APIs enable a finer controll and customization over each packet, and are used to implement traffic generators. For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK. Also, many of the listed traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.

@@

We have a large variety open-source tools available for custom traffic generation, but reproducing a realistic traffic scenario is a hard question. Selecting the right framework, a good traffic model, and the right configuration, is by itself a complex research project\cite{legotg-paper}\cite{selfsimilar-ethernet}. Since it is usually is not the main goal of the project, but just a mean, many times a simplistic and irrealistic sollution is opt because of the limited resources such as time and manpower.  Reproducig a realistic traffic usung these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation.

There are fewer sollutions on the open source community available that aim to fill this gap. Tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration. Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}. However they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration. Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic, and high throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}. Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library. The only way of replacing the traffic engine is changing and recompiling the original code. This is clearly a hard task\cite{legotg-paper}, and an error prone activity. Again, we fall in the same problem a complex task that usually is not the goal of the project.

Another issue is the large variety of tools, and different methods of configuration and limitations. To create a custom traffic, a user must read large manuals, and custom-design scripts. One of our bigger proposals is create a tool able to automatically do this processes. So The user may design his custom traffic by creating his own Compact Trace Descriptor, and create a traffic using many different tools, like Ostinato, D-ITG, Iperf, but not caring about how to proper configure each of them. In the table ~\ref{tab:related-work} we summarize our current scenario.

\begin{table}[ht!]
	\centering
	\caption{Current scenario of traffic generation}
	\scalebox{0.87}{
	\begin{tabular}{cccccc}
		\hline
		\rowcolor[HTML]{9B9B9B} 
		Sollution    & User Space  & Autoconfigurable & Realistic Traffic & Traffic Custumization & Extensibility \\ \hline
		Harpoon      & \textbf{no} & yes              & yes               & yes                   & \textbf{no}   \\
		\rowcolor[HTML]{C0C0C0} 
		D-ITG        & yes         & \textbf{no}      & yes               & yes                   & \textbf{no}   \\
		Swing        & yes         & yes              & yes               & \textbf{no}           & \textbf{no}   \\
		\rowcolor[HTML]{C0C0C0} 
		Ostinato     & yes         & \textbf{no}      & \textbf{no}       & yes                   & yes           \\
		LegoTG       & yes         & \textbf{no}      & \textbf{no}       & yes                   & yes           \\
		\rowcolor[HTML]{C0C0C0} 
		sourcesOnOff & yes         & \textbf{no}      & yes               & yes                   & \textbf{no}   \\
		Iperf        & yes         & \textbf{no}      & \textbf{no}       & yes                   & \textbf{no}   \\ \hline
	\end{tabular}
	}
	\label{tab:related-work}
\end{table}

@@

	\item Research the main apporoaches and methods found of the literature to create model Ethernet traffic, and for realistic traffic generation.

	\item Create a general method for modeling and parameterization of Ethernet traffic, aiming to mimic any traffic provided as input;

	\item Create a software able of \textit{learning} metrics from real network traffic, and based on the that reproduce it workload with similar (but not equal) characteristics, \textit{avoiding} the storage of \textit{pcap} files.

@@

	\item Traffic generation programmability: It must have what we call \textit{traffic generation progamability}. The compact trace descriptor must be simple and easy to read. In that way, the user may want to create his custom traffic, in a platform agnostic way. The traffic programmability must be flow-oriented;

>>>>

Emerging technologies such as SDN and NFV can be considered great promises that would drastically change the development and operation of computer networks. However, its enabling technologies such as virtualization still pose challenges as for performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior. Since it is expected that virtualization will affect performance negatively, these VNFs have to keep their degradation as small as possible. Therefore, guaranteeing the Service Layer Agreements becomes now a harder question. There is a demand for more reliable methods to ensure SLAs, over different types of loads.

It is already a well-known fact that the type of traffic used on performing tests matters. Studies show that  realistic Ethernet traffic provides different and variable load characteristics on routers\cite{harpoon-validation}, even with the same average bandwidth consumption. This fact indicates that tests that employ constant bit rate traffic generator tools are not enough for a complete validation of new technologies. There are many reasons for this behavior, which includes a grater traffic burstiness and variable packet sizes.

A burstier traffic can cause packet losses and buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}; thus degenerating network performance\footnote{Packet-trains periods and inter-packet times affect traffic burstiness}, and  measurement accuracy\cite{legotg-paper} \cite{background-traffic-matter}. Another key question is how applications will deal with packets, since it is a well-known fact that applications have a huge performance degradation in processing small packets\cite{comparative-trafficgen-tools}. A realistic synthetic traffic must not have a single one but rater use variable packet sizes \cite{packet-distribution-model}.

Furthermore realistic workload generators are an essential security research\cite{ditg-paper}, since generation of realistic workloads is important for evaluation of firewall middleboxes. It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}. Over a virtualized enviroment a realistic workload is expected to have an even larger inpact.

Another critical point is the flow-oriented operation of SDN networks, in which each new flow arriving on an SDN switch demands an extra communication with the controller, that may cause a bottleneck. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider. Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How VNFs and virtualized middle-boxes and SDN testbeds will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is a relevant subject.

@@

The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, so that each uses different methods of traffic generation, and enable controll of different features, such as: bits/bytes per second; packets per seconds; packet-sizes; protocols, header or payload customization; inter-packet times and On/Off periods; starting and sending time; and emulation of applications, such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.

Some traffic generator tools offer support emulation of single application workloads, however, this does not correspond to real complex scenarios. Other tools work as packet replay engines, such as TCPreplay and TCPivo. While is possible to produce a realistic workload at high rates using this tools, they comes with some drawbacks. Firstly, the storage space required becomes huge for long-term and high-speed traffic capture traces, lastly, obtaining good traffic traces is sometimes hard, due privacy issues and fewer good sources.

Many tools support a larger set of protocols and high-throughput for traffic generation, such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper}, sourcesOnOff\cite{sourcesonoff-paper}, and MoonGen. All of them offer a complex configuration framework, but its custumization is all up to the user. So, there is no simple way for the user to create a synthetic and realistic traffic scenario.

We also have a variety of APIs that enable the creation of traffic and custom packets, which include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others. These APIs provide a finer controll and customization over each packet, and are used to implement traffic generators. For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK. In addition, many of the listed traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.

@@

There is a  have a large variety of open-source tools available for custom traffic generation, but reproducing a realistic traffic scenario is a hard matter. Selecting the right framework, a good traffic model, and the right configuration, is by itself a complex research project\cite{legotg-paper}\cite{selfsimilar-ethernet}. Since it usually is not the main goal of the project, but just a mean of validation, many times a simplistic and unrealistic solution is selected due the limited resources such as time and labor.  Creating a realistic traffic through these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation.

There are few solutions on the open source community available that aiming to fill this gap, such as Harpoon\cite{harpoon-paper} and Swing\cite{swing-paper}.They capture traces to set internal parameters, providing an easier configuration. However they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration. Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic; so throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}. ecause its traffic generation engine is coupled to its modeling framework, you cannot opt to use a newer/faster packet generation library. The only way of replacing the traffic engine is changing and recompiling the original code which is a hard and  error prone activity\cite{legotg-paper}. Again, we fall in the same issue, a complex task that is usually not the goal of the project. In the table ~\ref{tab:related-work} we give a brief summary of what we have available on some open-source traffic-generators tools.

% Another matter is the large variety of tools, and different methods of configuration and its limitations. To create a custom traffic, a user must read large manuals, and custom-design scripts. One of our bigger proposals is create a tool able to automatically do this processes. So The user may design his custom traffic by creating his own Compact Trace Descriptor, and create a traffic using many different tools, like Ostinato, D-ITG, Iperf, but not caring about how to proper configure each of them. In the table ~\ref{tab:related-work} we summarize our current scenario.

\begin{table}[ht!]
	\centering
	\caption{Current scenario of traffic generation}
	\scalebox{0.87}{
	\begin{tabular}{cccccc}
		\hline
		\rowcolor[HTML]{9B9B9B} 
		Solution    & User Space  & Autoconfigurable & Realistic Traffic & Traffic Custumization & Extensibility \\ \hline
		Harpoon      & \textbf{no} & yes              & yes               & yes                   & \textbf{no}   \\
		\rowcolor[HTML]{C0C0C0} 
		D-ITG        & yes         & \textbf{no}      & yes               & yes                   & \textbf{no}   \\
		Swing        & yes         & yes              & yes               & \textbf{no}           & \textbf{no}   \\
		\rowcolor[HTML]{C0C0C0} 
		Ostinato     & yes         & \textbf{no}      & \textbf{no}       & yes                   & yes           \\
		LegoTG       & yes         & \textbf{no}      & \textbf{no}       & yes                   & yes           \\
		\rowcolor[HTML]{C0C0C0} 
		sourcesOnOff & yes         & \textbf{no}      & yes               & yes                   & \textbf{no}   \\
		Iperf        & yes         & \textbf{no}      & \textbf{no}       & yes                   & \textbf{no}   \\ \hline
	\end{tabular}
	}
	\label{tab:related-work}
\end{table}

@@

	\item Research the main apporoaches and methods found of the literature for realistic traffic generation.

	\item Create a general method for modeling and parameterization of Ethernet traffic;

	\item Create a self-configurable tool that observes and uses real network traffic, and try to mimic and reproduce its behavior characteristics, \textit{avoiding} the storage of \textit{pcap} files.

@@

	\item Traffic generation programmability: It must have what we call \textit{traffic generation progamability}. The compact trace descriptor must be simple and easy to read. That way, the user may want to create his custom traffic, in a platform agnostic way. The traffic programmability must be flow-oriented;
